---
title: "Markdown basic extra"
author: "Barry Bullas"
date: "21/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

no_rows<-nrow(mtcars)
library(plotly)
library(leaflet)
```

# The Dataset

This document will provide an overview of the **mtcars** dataset, a built in dataset within R Studio that can be used for practice.

This [Markdown cheat sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf) can be very *useful for guidance* when creating Markdown documents. 

## Summary Statistics

There are `r no_rows` rows in the dataset.

Below shows a summary of the overall dataset:

```{r cars, echo=FALSE}
summary(mtcars)
```

The first six rows of the dataset looks like this:

```{r preview, echo=FALSE}
head(mtcars)
```

## Including interactive plots
Where ggplot will insert a plot as a static image, plotly allows you to provide an interactive plot.  You can find out more about about plotly on the [plotly website](https://plot.ly/r/line-and-scatter/#new-to-plotly)

```{r plot, echo=FALSE, warnings=FALSE, message=FALSE}
p <- plot_ly(data = mtcars, x = ~wt, y = ~mpg) %>%
  layout(title = 'mtcars plot')
p
```

## The US home of motorcars

```{r}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=-83.0458, lat=42.3314, popup="The US home of the motorcar")
m  # Print the map
```

